Multi-Resolution Neural Field Estimation

### 2011-03-10 Multiresolution_framework/ltx/manuscript.tex
minor edits
final changes
made abstract less than 50 words

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Multi-Resolution Spatiotemporal Neural Field Estimation }

@@

\begin{abstract}
%\boldmath
The Integro-difference equation (IDE) is an increasingly popular model of spatio-temporal processes. Here we develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets. State and parameter estimation is performed using the Expectation Maximization (EM) algorithm. A synthetic example is provided
to demonstrate the framework.
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
% \begin{IEEEkeywords}
%  Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
%  \end{IEEEkeywords}
% For peer review papers, you can put extra information on the cover
% page as needed:
\ifCLASSOPTIONpeerreview
  \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
  \fi
%
%  For peerreview papers, this IEEEtran command inserts a page break and
%creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Multi-Resolution Neural Field Estimation }

@@

\begin{abstract}
%\boldmath
We develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets. State and parameter estimation is performed using the Expectation Maximization (EM) algorithm. A synthetic example is provided
to demonstrate the framework.
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
 \begin{IEEEkeywords}
  Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
  \end{IEEEkeywords}
% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
%   \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
%   \fi
%
%  For peerreview papers, this IEEEtran command inserts a page break and
%creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle
